method

### 2022-02-17 06_Paper/ER-ED/method.Rmd

@@

>>>>

# create variable "block"

data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neu"
data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"

@@

EMGLevView_aov <- afex::aov_ez(data = EMG_view,
                               id = "ID",
                               dv = "Lev",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)
